Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-15 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp_revised.tex
update supp

$\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy,
$T_{\mathrm{r}}$, is calculated from the electron and proton 4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.
The peak is not exactly at the deuteron binding energy because energy loss corrections have not been applied to the data nor SIMC. \\

>>>>

$T_{p}$ is the final proton kinetic energy and $T_{\mathrm{r}}$ is the recoil particle kinetic energy which is calculated from the electron and proton
4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron. The peak is not exactly at the deuteron binding energy because
energy loss corrections have not been applied to the data nor SIMC. \\
